\chapter{Testing}

Testing is an important phase in the development of any software project. It is essential to ensure that the system functions correctly and efficiently. The Rokers system was thoroughly tested to ensure that it meets the requirements and specifications set forth in the project. The following tests were performed:
\begin{enumerate}
    \item \textbf{Functionality test :} The functionality test is used to ensure that all the features of the system work correctly. The test includes checking the functionality of the server, the connection to the Spotify API, the music playback, and the database. The test was performed to ensure that the system can fetch music information and play music as expected.
    \item \textbf{Performance test :} The performance test is used to ensure that the system can handle a large number of requests and handle them efficiently. The test includes checking the response time of the system, the number of concurrent users that the system can handle, and the system's memory usage. The test was performed to ensure that the system can handle a large number of users without any issues.
    \item \textbf{Stress test :} The stress test is used to ensure that the system can handle a large number of concurrent users without any issues. The test includes checking the system's response time, the number of concurrent users that the system can handle, and the system's memory usage. The test was performed to ensure that the system can handle a high number of concurrent users without any issues.
    \item \textbf{Usability test :} The usability test is used to ensure that the system is easy to use and understand for the users. The test includes checking the user interface, the navigation, and the overall user experience. The test was performed to ensure that the system can be used easily and efficiently by the users.
    \item \textbf{Compatibility test :} The compatibility test is used to ensure that the system can run smoothly on different platforms and devices. The test includes checking the system on different operating systems, browsers, and devices. The test was performed to ensure that the system can be accessed by a wide range of users.
    
\end{enumerate}

The system passed all the tests successfully and was deemed ready for deployment.









