\chapter{Conclusion \& Future Enhancements}
\section{Conclusion}
In conclusion, Rokers is a innovative web application that allows users to share and listen to music together in real-time. Its unique synchronous playback feature allows everyone in a group to enjoy the same music at the same time, creating a fun and immersive listening experience.\\[0.1in] 

The user-friendly interface and wide range of supported music formats make it easy for anyone to join in and contribute to the playlist. Rokers is a great tool for bringing people together through their shared love of music, and we hope it will continue to bring joy and connection to its users for years to come.\\[0.1in]
\section{Future Enhancements}
Just like any other developer this project is the most basic website built using simple tools. We seek to increase the dynamic of the project by adding various other innovations to it. Such innovations would seem possible only with time, which we lack but regardless we strive to complete what we started.
\\

\textbf{We believe that apart from the present functionalities we can add : }
\begin{itemize}
    \item “Enhanced social features” Add options for users to connect with each other and interact within the app, such as chat rooms or the ability to follow other users and see their playlists.
    \item “Improved audio quality” Investigate ways to improve the audio quality of the music playback, such as by supporting high-resolution audio formats or integrating with audio enhancement technologies.
    \item “Improved search and discovery” Implement features to help users find new music to add to the playlist, such as personalized recommendations or integration with popular music streaming services.\\[0.1in]
    \item Apart from these changes we are open to various suggestions and hope to implement them soon so that this website can be used by the students for their needs.

\end{itemize}
